SCP Briefing Plots - Combined Intervention

### 2024-07-25 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Added a new working directory for laptop plotting

---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

>>>>

---
title: "SCP Briefing Plots - Combined Intervention"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
  pdf_document:
    toc: true
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```
